%! Author = kristofferpaulsson
%! Date = 2024-08-03

% Preamble
\documentclass[10pt,a4paper,notitlepage]{article}

\usepackage[margin=2.5cm]{geometry}
\usepackage{fontspec}
\usepackage[none]{hyphenat}  % --- NO HYPHENATION

\usepackage[hyphens]{xurl}  % --- URL HYPHENATION
\usepackage{hyperref}  % --- URL

\usepackage{draftwatermark}  % --- DONT-CITE

\urlstyle{same}  % --- URL
\pagenumbering{gobble}
\DraftwatermarkOptions{fontsize=2em,angle=0,vpos=1cm,color=black,text=Do Not Cite or Circulate}  % --- DONT-CITE

\usepackage{float}  % --- TABLE
\usepackage{makecell}  % --- TABLE
\usepackage{enumitem}  % --- LIST


\fontspec{Tinos}[
    Path = ../../font/t/,
    Extension = .ttf,
    UprightFont = *-Regular,
    Scale=1,
    Ligatures=TeX
]
\fontspec{Inter}[
    Path = ./../font/i/,
    Extension = .ttf ,
    UprightFont = *-Regular ,
    Scale=1,
    Ligatures=TeX
]

% Commands
\newcommand{\tsc}[1]{\textsc{#1}}
\newcommand*{\grc}[1]{\fontspec{Inter}#1\rmfamily}
\newcommand{\trc}[1]{\textit{\fontspec{Tinos}#1}}
\newcommand{\linkfoot}[3]{\footnote{\emph{#1}, s.v. ``{#2},'' accessed \printdate{#3}.}}

% Document
\begin{document}

    \subsection*{Ancient Greek: All Pronouns Listed}
    \begin{itemize}[label={}, leftmargin=0]
        \item Kristoffer E.D.\ Paulsson (2026), Independent Scholar.
    \end{itemize}

    \begin{itemize}
        \item The Personal Pronoun (Smyth, 1956:90, \S325).\ (w/o Homer \& Horodotus)
        \begin{itemize}
            \item First Person
            \item Second Person
            \item Third Person
        \end{itemize}
        \item The Intensive Pronoun (Smyth, 1956:92, \S327).
        \item Reflexive Pronouns (Smyth, 1956:93, \S329).
        \item Possessive Pronouns (Smyth, 1956:93, \S330).
        \item Reciprocal Pronoun (Smyth, 1956:94, \S331).
        \item The Definite Article (Smyth, 1956:94, \S332).
        \item Demonstrative Pronouns (Smyth, 1956:94, \S333).
        \begin{itemize}
            \item Proximal
            \item Medial
            \item Distal
        \end{itemize}
        \item Interrogative Pronouns (Smyth, 1956:95, \S334).
        \item Indefinite Pronouns (Smyth, 1956:95, \S334).
        \item Relative Pronouns (Smyth, 1956:96, \S338).
        \item Indefinite or General Relative Pronoun (Smyth, 1956:97, \S339).\ (w/o Homer \& Horodotus)
        \item Correlative Pronouns (Smyth, 1956:98, \S340).
    \end{itemize}

    \subsection*{Reference List}
    \begin{itemize}[label={}, leftmargin=0]
        %\item Ryd    \begin{itemize}[label={}, leftmargin=0]berg-Cox, J. (n.d.). \textit{LESSON XVII: Demonstrative Pronouns}. [online] A Digital Tutorial for Ancient Greek. Available at: \url{https://daedalus.umkc.edu/FirstGreekBook/JWW_FGB17.html} [Accessed 2 Feb. 2026].
        %\item Groton, A.H.\ (2013). \textit{From Alpha to Omega: a Beginning Course in Classical Greek}. Newburyport, Massachusetts: Focus Publishing.
        \item Smyth, H.W.\ (1956). \textit{Greek Grammar}. Cambridge, Massachusetts: Harvard University Press.
    \end{itemize}

\end{document}