%! Author = kristofferpaulsson
%! Date = 2024-08-03

% Preamble
\documentclass[10pt,a4paper,notitlepage]{article}

\usepackage[margin=2.5cm]{geometry}
\usepackage{fontspec}
\usepackage[none]{hyphenat}  % --- NO HYPHENATION

\usepackage[hyphens]{xurl}  % --- URL HYPHENATION
\usepackage{hyperref}  % --- URL

\usepackage{draftwatermark}  % --- DONT-CITE

\urlstyle{same}  % --- URL
\pagenumbering{gobble}
\DraftwatermarkOptions{fontsize=2em,angle=0,vpos=1cm,color=black,text=Do Not Cite or Circulate}  % --- DONT-CITE

\usepackage{float}  % --- TABLE
\usepackage{makecell}  % --- TABLE
\usepackage{enumitem}  % --- LIST


\fontspec{Tinos}[
    Path = ../../font/t/,
    Extension = .ttf,
    UprightFont = *-Regular,
    Scale=1,
    Ligatures=TeX
]
\fontspec{Inter}[
    Path = ./../font/i/,
    Extension = .ttf ,
    UprightFont = *-Regular ,
    Scale=1,
    Ligatures=TeX
]

% Commands
\newcommand{\tsc}[1]{\textsc{#1}}
\newcommand*{\grc}[1]{\fontspec{Inter}#1\rmfamily}
\newcommand{\trc}[1]{\textit{\fontspec{Tinos}#1}}
\newcommand{\linkfoot}[3]{\footnote{\emph{#1}, s.v. ``{#2},'' accessed \printdate{#3}.}}

% Document
\begin{document}

    \subsection*{Ancient Greek: Reflexive Pronouns in Third Person}
    \begin{itemize}[label={}, leftmargin=0]
        \item Kristoffer E.D.\ Paulsson (2026), Independent Scholar.
    \end{itemize}
    The third-person reflexive pronouns are formed by compounding the personal pronoun \grc{ἑ}, in the third-person
    accusative singular, with the corresponding oblique cases of the intensive pronoun \grc{αὐτός}.
    For example, combining \grc{ἑ} with \grc{αὐτοῦ} yields \grc{ἑαυτοῦ}; this formation applies across cases,
    numbers, and genders.

    Ayer (2018) says: ``Instead of \ldots \grc{ἑαυτοῦ}, etc., the contracted forms \ldots \grc{αὑτοῦ}, etc.,
    are also used.'' Therefore, as in the second-person reflexives, the third-person reflexive pronouns also exhibit
    contracted forms resulting from crasis, in which \grc{ε} is elided while the spiritus asper
    (rough breathing) is retained on the initial alpha, producing forms such as \grc{αὑτοῦ} (hautou).

    Smyth (1956:93, \S329 a) states ``For \grc{ἑαυτῶν}, etc., we find \grc{αὑτῶν}, \grc{αὑτοῖς}, \grc{-αῖς}, \grc{αὑτούς},
    \grc{-ά̄ς}. Distinguish \grc{αὑτοῦ} of himself from \grc{αὐτοῦ} (328).'' This suggests that the contracted plural
    forms exist in masculine and feminine for the dative and accusative cases, with no distinct neuter forms.

    \begin{table}[H]
        \begin{tabular}{c|ccc|c}
            & \multicolumn{3}{c|}{Sexus} & Genus \\
            & \tsc{Masc} & \tsc{Fem} & \tsc{Neu} & \tsc{M. F. N.} \\
            \hline
            \emph{\tsc{Singular}} & & & & \\
            \tsc{Nom} & -- & -- & -- & -- \\
            \tsc{Gen} & \makecell{\grc{ἑαυτοῦ} \trc{heautou} \\ \small of himself}
                    & \makecell{\grc{ἑαυτῆς} \trc{heautēs} \\ \small of herself}
                    & \makecell{\grc{ἑαυτοῦ} \trc{heautou} \\ \small of oneself}
                    & \makecell{( * ) \\ \small of itself} \\
            \tsc{Dat} & \makecell{\grc{ἑαυτῷ} \trc{heautōi} \\ \small to/for himself}
                    & \makecell{\grc{ἑαυτῇ} \trc{heautēi} \\ \small to/for herself}
                    & \makecell{\grc{ἑαυτῷ} \trc{heautōi} \\ \small to/for oneself}
                    & \makecell{( * ) \\ \small to/for itself} \\
            \tsc{Acc} & \makecell{\grc{ἑαυτόν} \trc{heauton} \\ \small himself}
                    & \makecell{\grc{ἑαυτήν} \trc{heautēn} \\ \small herself}
                    & \makecell{\grc{ἑαυτό} \trc{heauto} \\ \small oneself}
                    & \makecell{( * ) \\ \small itself} \\
            \hline
            \emph{\tsc{Dual}} & -- & -- & -- & -- \\
            \hline
            \emph{\tsc{Plural}} & & & & \\
            \tsc{Nom} & -- & -- & -- & -- \\
            \tsc{Gen} & \makecell{\grc{ἑαυτῶν} \trc{heautōn} \\ \small of themselves (m.)}
                    & \makecell{\grc{ἑαυτῶν} \trc{heautōn} \\ \small of themeslves (f.)}
                    & \makecell{\grc{ἑαυτῶν} \trc{heautōn} \\ \small of themselves (n.)}
                    & \makecell{( * ) \\ \small of these items} \\
            \tsc{Dat} & \makecell{\grc{ἑαυτοῖς} \trc{heautois} \\ \small to/for themselves (m.)}
                    & \makecell{\grc{ἑαυταῖς} \trc{heautais} \\ \small to/for themselves (f.)}
                    & \makecell{\grc{ἑαυτοῖς} \trc{heautois} \\ \small to/for themselves (n.)}
                    & \makecell{( * ) \\ \small to/for these items} \\
            \tsc{Acc} & \makecell{\grc{ἑαυτούς} \trc{heautous} \\ \small themselves (m.)}
                    & \makecell{\grc{ἑαυτάς} \trc{heautas} \\ \small themselves (f.)}
                    & \makecell{\grc{ἑαυτά} \trc{heauta} \\ \small themselves (n.)}
                    & \makecell{( * ) \\ \small these items} \\
        \end{tabular}
         \caption{Compiled from standard Ancient Greek grammars enhanced with transliteration and cues.
            Assume gender over sex except when the antecedent is a person.
             (Smyth, 1956:93, \S329)}
     \end{table}

    The third-person reflexive pronouns (\grc{ἑαυτοῦ}, \grc{-ῆς}, \grc{-οῦ}) exhibit full gender marking
    (masculine, feminine, neuter) because their referents may be any nominal, including inanimate or non-personal
    entities.
    By contrast, first- and second-person reflexives (\grc{ἐμαυτοῦ}/\grc{ἐμαυτῆς}, \grc{σεαυτοῦ}/\grc{σεαυτῆς})
    have only masculine and feminine forms and lack a neuter, since speakers and addressees are inherently animate and
    thus never neuter.

    \subsection*{Reference List}
    \begin{itemize}[label={}, leftmargin=0]
        \item Rydberg-Cox, J. (n.d.). \textit{LESSON XLVIII: Reflexive, Reciprocal, and Possessive Pronouns}. [online] A Digital Tutorial for Ancient Greek. Available at: \url{https://daedalus.umkc.edu/FirstGreekBook/JWW_FGB48.html} [Accessed 26 Mar. 2026].
        \item Ayer, M. ed., (2018). \textit{Goodell’s School Grammar of Attic Greek}. [online] Carlisle, Pennsylvania: Dickinson College Commentaries. Available at: \url{https://dcc.dickinson.edu/grammar/goodell/reflexive-pronouns} [Accessed 29 Mar. 2026].
        \item Smyth, H.W.\ (1956). \textit{Greek Grammar}. Cambridge, Massachusetts: Harvard University Press.
    \end{itemize}

\end{document}
